Checkpoint 3

### 2020-04-20 Checkpoint3.Rmd
Update Checkpoint3.Rmd

---
title: "Checkpoint 3"
author: ""
date: '`r format(Sys.Date(), "%B %d, %Y")`'
header-includes:
  - \usepackage{tabularx}
output:
  pdf_document: default
  html_document: default
abstract: ""
---

>>>>

---
title: "Checkpoint 3"
author: ""
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc:true
    toc_float:true
---

## About the Covid-tracking data sets
https://covidtracking.com/about-data
https://docs.google.com/spreadsheets/u/2/d/e/2PACX-1vRwAqp96T9sYYq2-i7Tj0pvTf6XVHjDSMIKBdZHXiCGGdNC0ypEU9NbngS8mxea55JuCFuua1MUeOj5/pubhtml
